\documentclass[10pt,letterpaper]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{tikz}
\usepackage{tabularx}

% Modern color scheme
\definecolor{accent}{HTML}{2B6CB0}
\definecolor{darktext}{HTML}{1A202C}
\definecolor{lighttext}{HTML}{4A5568}
\definecolor{ruleline}{HTML}{CBD5E0}

\setmainfont{Helvetica Neue}[
  BoldFont=Helvetica Neue Bold,
  ItalicFont=Helvetica Neue Italic
]

\hypersetup{colorlinks=true,linkcolor=accent,urlcolor=accent}
\color{darktext}
\pagestyle{plain}
\setlength{\parskip}{2pt}

\titleformat{\section}{\normalsize\bfseries\scshape\color{accent}}{}{0em}{}[{\color{ruleline}\titlerule}]
\titlespacing{\section}{0pt}{8pt}{4pt}
\setlist[itemize]{nosep,left=0pt..1.5em,topsep=1pt,label={\color{accent}\textbullet}}

\begin{document}

% Header
\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{accent} Jason Mimick}\\[4pt]
{\normalsize\color{lighttext} Product \& Engineering}\\[8pt]
{\small\color{lighttext}
540.359.5137 \enspace\textbar\enspace
\href{mailto:jmimick@gmail.com}{jmimick@gmail.com} \enspace\textbar\enspace
\href{https://github.com/jasonmimick}{github.com/jasonmimick} \enspace\textbar\enspace
\href{https://www.linkedin.com/in/jmimick}{linkedin.com/in/jmimick}}
\end{center}

\vspace{2pt}

\section{Professional Summary}
{\small Building and shipping revenue-generating products across a variety of technologies for over a quarter century.
Pragmatic, driven, hands-on, roll-up-sleeves attitude.
Database, cloud, devops, marketplace, product, \& engineering expertise with AI experience.
Graduate school and professional teaching.}

\section{Employment History}

\textbf{\href{https://aws.amazon.com/}{Amazon Web Services}} \hfill {\small\color{lighttext} New York, NY}\\
{\small\itshape\color{accent} WW Senior Partner Solutions Architect --- Observability, DevOps, GenAI \hfill May 2022 -- Present}
\begin{itemize}
\item {\small Enabling partner product integrations, launches, and go-to-market efforts for multiple partners across the entire suite of AWS services.}
\item {\small Working with top ISVs --- Core Member ISV TFC Datadog, Dynatrace, Hashicorp, Grafana and AWS service teams Bedrock, Lambda, ECS to deliver new integrations and solutions.}
\item {\small Next Gen Developer Tools Specialist --- Kiro, kiro-cli, MCP, ACP, Frontier Agents, DevOps Agent, Security Agent.}
\end{itemize}

\textbf{\href{https://www.mongodb.com/}{MongoDB, Inc}} \hfill {\small\color{lighttext} New York, NY}\\
{\small\itshape\color{accent} Product Manager Cloud \hfill Aug 2019 -- Jan 2022}
\begin{itemize}
\item {\small Kubernetes PM --- shipped official Helm Chart repository, MongoDB Atlas Kubernetes Operator, and Multi-Cluster support.}
\item {\small Launched MongoDB Atlas AWS \href{https://github.com/mongodb/mongodbatlas-cloudformation-resources}{CloudFormation Custom Resources} and \href{https://aws.amazon.com/quickstart/architecture/mongodb-atlas/}{Quickstart} --- grew from zero to 400+ clusters launched/month in 12 months.}
\end{itemize}

{\small\itshape\color{accent} Technical Director \hfill Aug 2017 -- Aug 2019}
\begin{itemize}
\item {\small Solo engineer for MongoDB Atlas GCP Enterprise Marketplace integration.}
\item {\small Enabled IBM to ship MongoDB in \href{https://www.ibm.com/products/cloud-pak-for-data}{Cloud Pak for Data}.}
\item {\small Kick-started MongoDB Kubernetes products with \href{https://cloud.redhat.com/blog/dev-preview-mongodb-enterprise-running-on-openshift}{Developer Preview}, sales support, and meetups.}
\item {\small PM for Cloud Foundry Tile --- migrated 400+ microservices to Atlas via \href{https://github.com/mongodb/atlas-osb}{Atlas Open Service Broker}.}
\end{itemize}

{\small\itshape\color{accent} Senior Consulting Engineer \hfill Jan 2015 -- Aug 2017}
\begin{itemize}
\item {\small Embedded consultant for United Airlines, The Gap, US Dept.\ of Veterans Affairs --- mobile apps, distribution workflow, data integrity.}
\end{itemize}

\textbf{\href{http://www.intersystems.com/}{InterSystems Corporation}} \hfill {\small\color{lighttext} Cambridge, MA}\\
{\small\itshape\color{accent} Sales Engineer \hfill May 2012 -- Dec 2014}
\begin{itemize}
\item {\small Technical expertise for global prospects from startups to \$10B+ corporations. Evangelized emerging cloud technologies.}
\end{itemize}

\textbf{\href{http://www.microsoft.com}{Microsoft Corporation}} \hfill {\small\color{lighttext} Redmond, WA}\\
{\small\itshape\color{accent} Senior Software Engineer Lead \hfill 2010 -- 2012}
\begin{itemize}
\item {\small Managed 7-engineer team for HealthVault Community Connect. Designed partner SDK. FDA Meaningful Use certification.}
\end{itemize}

{\small\itshape\color{accent} Senior Software Engineer \hfill 2008 -- 2010}
\begin{itemize}
\item {\small Built data ingestion engine for Amalga --- 4x implementation speedup. Extended Microsoft dev tools.}
\end{itemize}

\textbf{\href{http://www.quadramed.com/}{QuadraMed Corporation}} \hfill {\small\color{lighttext} Reston, VA}\\
{\small\itshape\color{accent} Enterprise Architect \hfill 2007 -- 2008}
{\small\enspace\textbar\enspace}
{\small\itshape\color{accent} Director Product Development \hfill 2005 -- 2007}
{\small\enspace\textbar\enspace}
{\small\itshape\color{accent} Principal Engineer / Team Lead \hfill 2002 -- 2005}
{\small\enspace\textbar\enspace}
{\small\itshape\color{accent} Programmer/Analyst II \hfill 2000 -- 2002}
\begin{itemize}
\item {\small 8 years progressing from analyst to enterprise architect. Managed 17-person team. Built HL7 messaging, web portals, biometric auth, SSO, and BI systems.}
\end{itemize}

{\small\textbf{University of Memphis} --- \textit{\color{accent}Graduate Teaching Fellow, 1999--2000} \enspace\textbar\enspace \textbf{IDX Systems} --- \textit{\color{accent}Software Engineer, 1998--2000}}

\section{Technical Skills}
\begin{tabularx}{\textwidth}{@{}r X@{}}
{\small\bfseries\color{accent} Languages} & {\small Go, Python, Java, C\#, JavaScript/TypeScript, Shell, SQL, \LaTeX} \\
{\small\bfseries\color{accent} GenAI} & {\small Amazon Bedrock, Bedrock Agents, AgentCore, Strands SDK, LangChain, LangGraph, Nova Sonic, MCP, ACP, RAG, LLM Observability} \\
{\small\bfseries\color{accent} Observability} & {\small OpenTelemetry, ADOT, Dynatrace, Datadog, Jaeger, CloudWatch, Grafana, Davis AI} \\
{\small\bfseries\color{accent} AWS} & {\small Lambda, ECS/Fargate, CDK, CloudFormation, AppConfig, API Gateway, S3, SageMaker, SSM, IAM, ECR, CodePipeline} \\
{\small\bfseries\color{accent} Tools} & {\small Kiro, Docker, Terraform, Helm, Git, Obsidian} \\
{\small\bfseries\color{accent} Platforms} & {\small Kubernetes, Cloud Foundry, OpenShift, Crossplane, Linux, macOS} \\
{\small\bfseries\color{accent} Data} & {\small MongoDB Atlas, DynamoDB, OpenSearch, PostgreSQL, HL7/FHIR} \\
{\small\bfseries\color{accent} Portfolio} & {\small \href{https://github.com/jasonmimick/portfolio}{github.com/jasonmimick/portfolio}} \\
\end{tabularx}

\section{Education}
\textbf{University of Vermont} --- MS Mathematics, 1998 \enspace\textbar\enspace Thesis: \href{http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.28.2960&rep=rep1&type=pdf}{Ranking Partially Ordered Sets} \enspace\textbar\enspace Graduate Teaching Fellow --- Algebra, Calculus, Discrete Mathematics\\
\textbf{University of Nebraska} --- BS Mathematics, 1996

\section{Patent}
{\small Serviceability and Configuration Management --- United States 20100299653}

\section{Personal Interests}
{\small Family, Music (Guitar-head), Philosophy, Math, Technology, Cycling, Running, Hiking, \& our dog Luna and crazy cats Aslan and Ali}

\end{document}
