\documentclass[10pt,letterpaper]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}

\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}
\pagestyle{plain}
\setlength{\parskip}{2pt}
\titleformat{\section}{\normalsize\bfseries\scshape}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{3pt}
\setlist[itemize]{nosep,left=0pt..1.5em,topsep=1pt}

\begin{document}

\begin{center}
{\LARGE\bfseries Jason Mimick}\\[4pt]
{\large Product \& Engineering}\\[6pt]
540.359.5137 \quad
\href{mailto:jmimick@gmail.com}{jmimick@gmail.com} \quad
\href{https://github.com/jasonmimick}{github.com/jasonmimick} \quad
\href{https://www.linkedin.com/in/jmimick}{linkedin.com/in/jmimick}
\end{center}

\section{Professional Summary}
Building and shipping revenue-generating products across a variety of technologies for over a quarter century.
Pragmatic, driven, hands-on, roll-up-sleeves attitude.
Database, cloud, devops, marketplace, product, \& engineering expertise with AI experience.
Graduate school and professional teaching.

\section{Employment History}

\textbf{\href{https://aws.amazon.com/}{Amazon Web Services}} --- New York, New York USA\\
\textit{WW Senior Partner Solutions Architect -- Observability, DevOps, GenAI \hfill May 2022 -- Present}
\begin{itemize}
\item Enabling partner product integrations, launches, and go-to-market efforts for multiple partners across the entire suite of AWS services.
\item Working with top ISVs -- Core Member ISV TFC Datadog, Dynatrace, Hashicorp, Grafana and AWS service teams Bedrock, Lambda, ECS to deliver new integrations and solutions.
\item Next Gen Developer Tools Specialist -- Kiro, kiro-cli, MCP, ACP, Frontier Agents, DevOps Agent, Security Agent.
\end{itemize}

\textbf{\href{https://www.mongodb.com/}{MongoDB, Inc}} --- New York, New York USA\\
\textit{Product Manager Cloud \hfill Aug 2019 -- Jan 2022}
\begin{itemize}
\item As the Kubernetes PM at MongoDB I shipped the official Helm Chart repository, a MongoDB Atlas Kubernetes Operator, and support for Multi-Cluster.
\item Launched the MongoDB Atlas AWS \href{https://github.com/mongodb/mongodbatlas-cloudformation-resources}{CloudFormation Custom Resources} and \href{https://aws.amazon.com/quickstart/architecture/mongodb-atlas/}{Quickstart} which grew from zero users to over 400 clusters launched per month over a 12 month period.
\end{itemize}

\textit{Technical Director \hfill Aug 2017 -- Aug 2019}
\begin{itemize}
\item Solo engineer and maintainer for MongoDB Atlas GCP Enterprise Marketplace integration.
\item Supported and enabled IBM to ship support for MongoDB in \href{https://www.ibm.com/products/cloud-pak-for-data}{Cloud Pak for Data}.
\item Kick-started official MongoDB Kubernetes products with a \href{https://cloud.redhat.com/blog/dev-preview-mongodb-enterprise-running-on-openshift}{Developer Preview}, sales support, outreach, and meetups.
\item Product Manager for MongoDB Cloud Foundry Tile -- helped customers migrate 400+ microservices to MongoDB Atlas via an \href{https://github.com/mongodb/atlas-osb}{Atlas Open Service Broker}.
\end{itemize}

\textit{Senior Consulting Engineer \hfill Jan 2015 -- Aug 2017}
\begin{itemize}
\item Embedded dedicated consultant for United Airlines, The Gap, and the US Dept.\ of Veterans Affairs -- delivered projects for mobile apps, distribution workflow, and data integrity.
\item Delivered on-site technical training, consultation, and support across numerous industries.
\end{itemize}

\textbf{\href{http://www.intersystems.com/}{InterSystems Corporation}} --- Cambridge, Massachusetts USA\\
\textit{Sales Engineer \hfill May 2012 -- Dec 2014}
\begin{itemize}
\item Provided technical expertise for global prospects ranging from startups to \$10B+ corporations.
\item Evangelized and educated internal and external customers on emerging cloud technologies.
\end{itemize}

\textbf{\href{http://www.microsoft.com}{Microsoft Corporation}} --- Redmond, Washington USA\\
\textit{Senior Software Engineer Lead \hfill 2010 -- 2012}
\begin{itemize}
\item Managed development team of 7 engineers for Microsoft HealthVault Community Connect.
\item Designed, built, and evangelized a partner software development kit.
\item Certified products for FDA Meaningful Use healthcare reform requirements.
\end{itemize}

\textit{Senior Software Engineer \hfill 2008 -- 2010}
\begin{itemize}
\item Built a data ingestion engine and developer tools for Amalga speeding up implementations by a factor of 4.
\item Extended Microsoft development tools for repeatable and verifiable data processing.
\end{itemize}

\textbf{\href{http://www.quadramed.com/}{QuadraMed Corporation}} --- Reston, Virginia USA\\
\textit{Enterprise Architect \hfill 2007 -- 2008}
\begin{itemize}
\item Advised leadership team on strategic technology plans.
\item Delivered architectural blueprints for single-sign-on, workflow, and business intelligence projects.
\end{itemize}

\textit{Director Product Development \hfill 2005 -- 2007}
\begin{itemize}
\item Managed a team of 17 designers, engineers, testers, and writers using agile methods.
\item Managed app development platform, person indexing, workflow, front-end GUI, and content management products.
\end{itemize}

\textit{Principal Software Engineer / Team Lead \hfill 2002 -- 2005}
\begin{itemize}
\item Developed a hospital consumer web portal application.
\item Designed and built a Java HL7 enterprise messaging system.
\item Integrated biometric and LDAP authentication systems into existing products.
\end{itemize}

\textit{Programmer/Analyst II \hfill 2000 -- 2002}
\begin{itemize}
\item HL7 CCOW enabled products and developed bi-directional HL7 interfaces.
\item Conducted training courses on proprietary 4GL programming language.
\end{itemize}

\textbf{University of Memphis} --- Memphis, Tennessee USA\\
\textit{Graduate Teaching Fellow \hfill 1999 -- 2000}
\begin{itemize}
\item Lectured university algebra, calculus, and discrete mathematics courses.
\end{itemize}

\textbf{IDX Systems Corporation} --- Burlington, Vermont USA\\
\textit{Software Engineer \hfill 1998 -- 2000}
\begin{itemize}
\item Designed and coded Mumps database scripts and HL7 interfaces for IDX clients.
\end{itemize}

\section{Technical Skills}
\textbf{Languages:} Go, Python, Java, C\#, JavaScript/TypeScript, Shell, SQL, \LaTeX\\
\textbf{GenAI \& Agents:} Amazon Bedrock, Bedrock Agents, Bedrock AgentCore, Strands Agents SDK, LangChain, LangGraph, Nova Sonic, MCP, ACP, Prompt Engineering, RAG, LLM Observability\\
\textbf{Observability:} OpenTelemetry (OTEL), ADOT, Dynatrace, Datadog, Jaeger, CloudWatch, Grafana, LLM Tracing, Davis AI\\
\textbf{AWS:} Lambda, ECS/Fargate, CDK, CloudFormation, AppConfig, API Gateway, S3, SageMaker, SSM, IAM, ECR, CodePipeline\\
\textbf{Developer Tools:} Kiro, kiro-cli, Docker, Terraform, Helm, Git, Obsidian, Pandoc\\
\textbf{Platforms:} Kubernetes, Cloud Foundry, OpenShift, Crossplane, Linux, macOS\\
\textbf{Data:} MongoDB Atlas, DynamoDB, OpenSearch, PostgreSQL, HL7/FHIR\\
\href{https://github.com/jasonmimick/portfolio}{Portfolio}

\section{Education}
\textbf{University of Vermont} --- MS Mathematics, 1998\\
Master's Thesis: \href{http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.28.2960&rep=rep1&type=pdf}{Ranking Partially Ordered Sets}. Graduate Teaching Fellow -- Algebra, Calculus, and Discrete Mathematics.

\textbf{University of Nebraska} --- BS Mathematics, 1996

\section{Patents}
Serviceability and Configuration Management --- United States 20100299653

\section{Personal Interests}
Family, Music (Guitar-head), Philosophy, Math, Technology, Cycling, Running, Hiking, \& our dog Luna and crazy cats Aslan and Ali

\end{document}
